\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}

%基本資訊

\noindent
Title:Facilitating the Process Rate of Difference Determination within HTML after Events Triggered in Web Page\\
Pages: 40\\
School: National Taipei University of Technology\\
Department: Computer Science and Information Engineering\\
Time: July, 2022\\
Degree: Master\\
Researcher: Yu-Siang Liao\\
Advisor: Shou-Han Chen, \emph{Ph. D.}
\hspace*{\fill}\\
Keywords: HTML, HTML comparison, Automated acceptance tests, Browser extension tool\\
\hspace*{\fill}\\
\indent
Writing automated web testing scripts mainly uses programs to simulate the situation of users operating web pages.
In order to determine whether the interactive components in the website are normally triggered, 
a part of the changed HTML content will be used as the judging condition for the success of the interaction.
Testers make it difficult to find stable element constraints in an efficient way because components change rapidly or only focus on the current component changes.

This thesis proposes to use the HTML text comparison method to develop a browser extension package that uses in the browser developer tools.
Testers can get all the differences in the panel of browser developer tools if the detail of the element is changed because of interactive components.
In order to maintain HTML content after interacting and reduce the unnecessary compared results, we designed with timing and filtering functions additionally.

The three major functions of the extension will allow developers to reduce the XPath length and durability according to the results, thereby increasing the program stability.